Research training portfolio

### 2012-12-20 Research training portfolio.tex
RTP: fixed typos, RP: deleted comments

\subsubsection{Lexicon module (context-free)}
Google provided us with an enormous list of word frequencies on the internet in 2008. The LexiconChecker checks for every word in the input whether there's a word on the frequencylist that is very similar to it, but much more frequent.

@@

\subsubsection{Most modules didn't provide confidences measures} \label{formulas}
Implementing the confidence slider described above was a hard and labor-intensive process. Not only did I have to create a working slider in Javascript that behaved like expected in all browsers, this slider also had to look like Monica had envisioned it, and the position of the handle had to be linked to both the errors marked in the text and the errors in the menu (directly above the slider). Before this could work, however, the slider needed to be able to extract the confidence for each error from Fowlt's output xml. This information about confidence originally wasn't there either, so I had to tell the process chain to ask each module for this information, and add it to the right place in the output. All modules subsequently had to be changed so they actually did return their confidence for each error. In other words, imlementing the slider was a long journey that made me revisit all layers of Fowlt's architecture.\\\indent
The biggest problem in this process, however, is that most modules not only didn't return some confidence measure for each error, they actually didn't calculate one. This not only meant I had to go back to the C-code of the original modules, but also that I had to come up with formulas to represent exactly how confident the modules are. I would like to use this final subsection to explain in detail the formulas I have chosen:

@@

\paragraph{Step 3: Error correction.} Detecting an error is of course something different from correctly correcting it. That is, when a spelling checker corrects 'i like you alot' into 'i like you allot' it might have detected the error, but replaced it with the wrong word. If approriate corrections is what the user is interested in, it is possible to only count as true positives the errors correctly corrected, while the incorrectly corrected errors are counted as false positives. From the resulting correction confusion matrix the measures correction accuracy, correction recall, correction precision and correction F-score can then be calculated again. \\\indent
For this paper, the correction measures will always be identical to the detecion measures, and will therefore not be mentioned seperately. This is because only two-option confusibles are investigated, which means that the approriate correction is always 'the other option' once an error is detected correctly. This of course does not hold for confusibles with three or more options, like \emph{to} versus \emph{too} versus \emph{two} or \emph{they're} versus \emph{there} versus \emph{their}.

\paragraph{Simulating errors.} In the description of these measures, I have assumed the existence of a text corpus full of annotated natural errors, so we can easily see which errors were correctly identified, and which were missed. Such a corpus unfortunately does not exist, and because of time and money constraints I was unable to create one myself. To solve this, such a corpus was created artificially by adding errors to 10\% of the examples used for evaluation. I would like to stress, however, that this is a dangerous approach: by adding artifical errors one risks adding very unnatural errors, making the evaluation results different from real usage results, and thus less useful. \\\indent
Fortunately, our focus on confusibles largely eliminates this problem: we don't only already know which words are often spelled wrong, we also know \emph{how} language users spell them wrong (unlike, for example, typos). A problem that still remains, though, is the fact that some errors are not made as often as others. For example, "your" might be used instead of "you're" much more than vice versa; \citet{sfd99} for example claim that confusible errors are largely based on frequencies. Research into the occurence frequencies for all confusible errors would be needed to be able to simulate errors in a more natural way.

@@

\section{General conclusion}
In this research training portfolio, I hope to have shown that creating a spelling corrector isn't something that can be done in a day, even if most of the code is already available. I didn't only change what was there to work with English, I also had to solve several problems related to processing the English language, extend the software on some places (for example, with the confidence slider), and did a little study on the confusible correctors' training data. While doing this, I also had to get familiar with new concepts (SSH, GitHub, MBL) on an almost daily basis.\\\indent
Perhaps suprisingly, the fact that I have created something which could (hopefully) be useful to hundreds, if not thousands or millions of people around the globe, and the fact that I have gathered lots of new and super useful knowledge, are not the most valuable things I got out of this internship. The most valuable thing is that I rediscovered language technology as something I love, and that I now know what I want to spend my future doing.

@@

\bibitem[Agirre et al., 1998]{agirre98}
Agirre, E., K. Gojenola, K. Sarasola, \& A. Voutilainen (1998). Towards a Single Proposal in Spelling Correction. \emph{COLING-ACL ’98},  22-28.
\bibitem[Brill \& Moore, 2000]{bm00}
Brill, E. \& R. C. Moore (2000). An improved error model for noisy channel spelling correction. In \emph{Proceedings of the 38th Annual Meeting of the ACL}, 286-293.
\bibitem[Daelemans, Van den Bosch \& Weijters(1997)]{dvdbw97}
Daelemans, W., A. van den Bosch, \& A. Weijters (1997). IGTree: using trees for compression and classification in lazy learning algorithms. \emph{Artificial Intelligence Review, 11}, 407–423.
\bibitem[Van Delden et al., 2004]{vandelden04}
Van Delden, S., D. B. Bracewell, \& F. Gomez (2004). Supervised and unsupervised automatic spelling correction algorithms. In D. Zhang, E. Gregoire \& D. DeGroot (eds), \emph{Proceedings of the 2004 IEEE International Conference on Information Reuse and Integration}, 530–535, Las Vegas.
\bibitem[Fawcett, 2004]{fawcett04}
Fawcett, T. (2004). \emph{ROC Graphs: Notes and Practical Considerations for Researchers.} Available online at binf.gmu.edu/mmasso/ROC101.pdf.
\bibitem[Garcia \& Herrera, 2009]{gh09}
Garcia, S. \& F. Herrera (2009). Evolutionary Undersampling for Classification with Imbalanced Datasets: Proposals and Taxonomy. \emph{Evolutionary Computation 17}, 275-306.
\bibitem[He \& Garcia, 2009]{hg09}
He, H. \& E. Garcia (2009). Learning from imbalanced data. \emph{IEEE Transactions on knowledge and data engineering, 21(9)}, 1263-1281.
\bibitem[Van Hulse, Khoshgoftaar \& Napolitano(2007)]{vhkn07}
Van Hulse, J. T. M. Khoshgoftaar \& A. Napolitano (2007). Experimental Perspectives on Learning from Imbalanced Data. \emph{Proceedings of the 24 th International Conference on Machine Learning.}
\bibitem[Pollock \& Zamora, 1984]{pz84}
Pollock J. J. \& A. Zamora (1984). Automatic spelling correction in scientific and scholarly text. \emph{Commun. ACM, 27(4)}, 358-368.
\bibitem[Provost, ?]{provost}
Provost, F. (year unkown). \emph{Machine Learning from Imbalanced Data Sets 101.} Extended abstract.
\bibitem[Reynaert, 2008]{reynaert08}
Reyneart, M. (2008). All, and only, the errors: More complete and consistent spelling and OCR-error correction evaluation. \emph{Proceedings of the Sixth International Language Resources and Evaluation (LREC’08), Marrakech, Morocco}.
\bibitem[Sandra et al., 1999]{sfd99}
Sandra, D., Frisson, S.,Daems, F., (1999). Why simple verb forms can be so difficult to spell: the influence of homophone frequency and distance in Dutch. \emph{Brain Language, 68(1-2),} 277-283.
\bibitem[Starlander \& Popescu-Belis, 2002]{sp02}
Starlander, M. \& A. Popescu-Belis (2002). Corpusbased evaluation of a French spelling and grammar checker. In \emph{LREC 2002: Third International Conference on language resources and evaluation, volume 1}, 268–274. Paris: ELRA, European Language Resources.
\bibitem[Toutanova \& Moore, 2002]{tm02}
Toutanova, K. \& R. C. Moore (2002). Pronunciation modeling for improved spelling correction. In \emph{Proceedings of the 40th Annual Meeting of the ACL}, 144–151.

>>>>

\subsubsection{Lexicon module (context-free)}
Google provided us with an enormous list of word frequencies on the internet in 2008. The LexiconChecker checks for every word in the input whether there's a word on the frequency list that is very similar to it, but much more frequent.

@@

\subsubsection{Most modules didn't provide confidences measures} \label{formulas}
Implementing the confidence slider described above was a hard and labor-intensive process. Not only did I have to create a working slider in Javascript that behaved like expected in all browsers, this slider also had to look like Monica had envisioned it, and the position of the handle had to be linked to both the errors marked in the text and the errors in the menu (directly above the slider). Before this could work, however, the slider needed to be able to extract the confidence for each error from Fowlt's output xml. This information about confidence originally wasn't there either, so I had to tell the process chain to ask each module for this information, and add it to the right place in the output. All modules subsequently had to be changed so they actually did return their confidence for each error. In other words, implementing the slider was a long journey that made me revisit all layers of Fowlt's architecture.\\\indent
The biggest problem in this process, however, is that most modules not only didn't return some confidence measure for each error, they actually didn't calculate one. This not only meant I had to go back to the C-code of the original modules, but also that I had to come up with formulas to represent exactly how confident the modules are. I would like to use this final subsection to explain in detail the formulas I have chosen:

@@

\paragraph{Step 3: Error correction.} Detecting an error is of course something different from correctly correcting it. That is, when a spelling checker corrects 'i like you alot' into 'i like you allot' it might have detected the error, but replaced it with the wrong word. If appropriate corrections is what the user is interested in, it is possible to only count as true positives the errors correctly corrected, while the incorrectly corrected errors are counted as false positives. From the resulting correction confusion matrix the measures correction accuracy, correction recall, correction precision and correction F-score can then be calculated again. \\\indent
For this paper, the correction measures will always be identical to the detecion measures, and will therefore not be mentioned separately. This is because only two-option confusibles are investigated, which means that the appropriate correction is always 'the other option' once an error is detected correctly. This of course does not hold for confusibles with three or more options, like \emph{to} versus \emph{too} versus \emph{two} or \emph{they're} versus \emph{there} versus \emph{their}.

\paragraph{Simulating errors.} In the description of these measures, I have assumed the existence of a text corpus full of annotated natural errors, so we can easily see which errors were correctly identified, and which were missed. Such a corpus unfortunately does not exist, and because of time and money constraints I was unable to create one myself. To solve this, such a corpus was created artificially by adding errors to 10\% of the examples used for evaluation. I would like to stress, however, that this is a dangerous approach: by adding artificial errors one risks adding very unnatural errors, making the evaluation results different from real usage results, and thus less useful. \\\indent
Fortunately, our focus on confusibles largely eliminates this problem: we don't only already know which words are often spelled wrong, we also know \emph{how} language users spell them wrong (unlike, for example, typos). A problem that still remains, though, is the fact that some errors are not made as often as others. For example, "your" might be used instead of "you're" much more than vice versa; \citet{sfd99} for example claim that confusible errors are largely based on frequencies. Research into the occurrence frequencies for all confusible errors would be needed to be able to simulate errors in a more natural way.

@@

\section{General conclusion}
In this research training portfolio, I hope to have shown that creating a spelling corrector isn't something that can be done in a day, even if most of the code is already available. I didn't only change what was there to work with English, I also had to solve several problems related to processing the English language, extend the software on some places (for example, with the confidence slider), and did a little study on the confusible correctors' training data. While doing this, I also had to get familiar with new concepts (SSH, GitHub, MBL) on an almost daily basis.\\\indent
Perhaps surprisingly, the fact that I have created something which could (hopefully) be useful to hundreds, if not thousands or millions of people around the globe, and the fact that I have gathered lots of new and super useful knowledge, are not the most valuable things I got out of this internship. The most valuable thing is that I rediscovered language technology as something I love, and that I now know what I want to spend my future doing.

@@

\bibitem[Agirre et al., 1998]{agirre98}
Agirre, E., K. Gojenola, K. Sarasola, \& A. Voutilainen (1998). Towards a Single Proposal in Spelling Correction. \emph{COLING-ACL ’98},  22-28.
\bibitem[Brill \& Moore, 2000]{bm00}
Brill, E. \& R. C. Moore (2000). An improved error model for noisy channel spelling correction. In \emph{Proceedings of the 38th Annual Meeting of the ACL}, 286-293.
\bibitem[Daelemans, Van den Bosch \& Weijters(1997)]{dvdbw97}
Daelemans, W., A. van den Bosch, \& A. Weijters (1997). IGTree: using trees for compression and classification in lazy learning algorithms. \emph{Artificial Intelligence Review, 11}, 407–423.
\bibitem[Van Delden et al., 2004]{vandelden04}
Van Delden, S., D. B. Bracewell, \& F. Gomez (2004). Supervised and unsupervised automatic spelling correction algorithms. In D. Zhang, E. Gregoire \& D. DeGroot (eds), \emph{Proceedings of the 2004 IEEE International Conference on Information Reuse and Integration}, 530–535, Las Vegas.
\bibitem[Fawcett, 2004]{fawcett04}
Fawcett, T. (2004). \emph{ROC Graphs: Notes and Practical Considerations for Researchers.} Available online at binf.gmu.edu/mmasso/ROC101.pdf.
\bibitem[Garcia \& Herrera, 2009]{gh09}
Garcia, S. \& F. Herrera (2009). Evolutionary Undersampling for Classification with Imbalanced Datasets: Proposals and Taxonomy. \emph{Evolutionary Computation 17}, 275-306.
\bibitem[He \& Garcia, 2009]{hg09}
He, H. \& E. Garcia (2009). Learning from imbalanced data. \emph{IEEE Transactions on knowledge and data engineering, 21(9)}, 1263-1281.
\bibitem[Van Hulse, Khoshgoftaar \& Napolitano(2007)]{vhkn07}
Van Hulse, J. T. M. Khoshgoftaar \& A. Napolitano (2007). Experimental Perspectives on Learning from Imbalanced Data. \emph{Proceedings of the 24 th International Conference on Machine Learning.}
\bibitem[Pollock \& Zamora, 1984]{pz84}
Pollock J. J. \& A. Zamora (1984). Automatic spelling correction in scientific and scholarly text. \emph{Commun. ACM, 27(4)}, 358-368.
\bibitem[Provost, ?]{provost}
Provost, F. (year unknown). \emph{Machine Learning from Imbalanced Data Sets 101.} Extended abstract.
\bibitem[Reynaert, 2008]{reynaert08}
Reyneart, M. (2008). All, and only, the errors: More complete and consistent spelling and OCR-error correction evaluation. \emph{Proceedings of the Sixth International Language Resources and Evaluation (LREC’08), Marrakech, Morocco}.
\bibitem[Sandra et al., 1999]{sfd99}
Sandra, D., Frisson, S.,Daems, F., (1999). Why simple verb forms can be so difficult to spell: the influence of homophone frequency and distance in Dutch. \emph{Brain Language, 68(1-2),} 277-283.
\bibitem[Starlander \& Popescu-Belis, 2002]{sp02}
Starlander, M. \& A. Popescu-Belis (2002). Corpusbased evaluation of a French spelling and grammar checker. In \emph{LREC 2002: Third International Conference on language resources and evaluation, volume 1}, 268–274. Paris: ELRA, European Language Resources.
\bibitem[Toutanova \& Moore, 2002]{tm02}
Toutanova, K. \& R. C. Moore (2002). Pronunciation modeling for improved spelling correction. In \emph{Proceedings of the 40th Annual Meeting of the ACL}, 144–151.
